econ

### 2024-01-07 index.qmd
buildinstall
an

---
title: ""
output: github_document
always_allow_html: true
execute: 
  cache: false
filters:
  - webr
---

# Manifold Destiny - or how to rig an election
**Based upon the ideas developed by Edward K. Solomon**
![](pngs/md.png)
tidyr

>>>>

---
title: ""
output: github_document
always_allow_html: true
execute: 
  cache: false
filters:
  - webr
format: 
  html:
    css: "https://kineticgraphs.org/css/kg.0.2.7.css"
    include-in-body:
          - text: |
              <script src="https://kineticgraphs.org/js/kg.0.2.7.js"></script>
---

# Manifold Destiny - or how to rig an election
**Based upon the ideas developed by Edward K. Solomon**
![](pngs/md.png)
